\LARGE \bf A Formal Description of Bitcoin's Script Language

### 2017-03-19 paper.tex
added difficulty encountered to {Application of Script Grammar}

>>>>

1) It was our hope that we could define operational semantics for op codes of previous versions of Script that caused crashes or other issues in the past.  Using these definitions, we would then show that the old definitions could be used to cause problems.  Unfortunately, there is very little documentation regarding how these errors came about.  The reference documentation itself only documents changes back to 2014 while most of the serious problems with Script were fixed in 2010. The only fix we were able to analyze was the change to OP\_RETURN.
